### 2023-10-21 README.Rmd
new readme file - 231021 v2

<li>`turf()`: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect product bundle based on the reach (e.g., how many participants consider buying at least one product of that assortment) and the frequency (how many products are on average a purchase option). `turf()` currently provides both the *threshold*  approach (`approach = 'thres'`; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p. 112) and the *first choice* approach (`approach = 'fc'`; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p. 111).</li>

<li>`freqassort()`: Similar to `turf()`, `freqassort()`
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment. 
Again, you have to define a `none` alternative, because `freqassort()` uses 
the <i>threshold</i> approach, meaning if the utility of one product is above 
the utility of `none`, it is marked as potential purchase option. 
While `turf()` calculates the reach and frequency for <b>all</b> combinations, 
you specify the combination you are interested in `freqassort()`.</li>

<li>`reach()`: Similar to `turf()`, `reach()` will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. `reach()` also uses the <i>threshold</i> approach (see above). While `turf()` calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in `reach()`.</li>

<li>`marksim()`: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>

@@

> <b>Important</b>: For both `reach()` and `freqassort()`, `none` does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.

@@

<li>`ACBC`: Example data set with raw utilities of an ACBC
study conducted in Sawtooth. Price was linear-coded while the other
attributes were coded as part-worths.

<li>`ACBC_interpolate`: Example data set with raw utilities
of an ACBC study conducted in Sawtooth. Price was piecewise-coded,
another attribute was linear-coded while the other attributes were coded
as part-worths.</li>

<li>`CBC`: Example data set with raw utilities of a CBC
study conducted in Sawtooth. All attributes were coded as
part-worth.</li>

<li>`CBC_lin`: Example data set with raw utilities of a CBC
study conducted in Sawtooth. One attribute was linear coded while the
other attributes are part-worth coded.</li>

<li>`MaxDiff`: Example data set with raw utilities of a
MaxDiff study conducted in Sawtooth.</li>

>>>>

<li><code>turf()</code>: <b>T</b>(otal) <b>U</b>(nduplicated) <b>R</b>(each) and <b>F</b>(requency) is a "product line extension model" (Miaoulis et al., 1990, p. 29) that helps to find the perfect product bundle based on the reach (e.g., how many participants consider buying at least one product of that assortment) and the frequency (how many products are on average a purchase option). <code>turf()</code> currently provides both the *threshold*  approach (<code>approach = 'thres'</code>; all products that exceed a threshold are considered, e.g., a purchase option; Chrzan & Orme, 2019, p. 112) and the *first choice* approach (<code>approach = 'thres'</code>; only product with highest utility is considered as purchase option; Chrzan & Orme, 2019, p. 111).</li>

<li><code>freqassort()</code>: Similar to <code>turf()</code>, <code>freqassort()</code>
will give you the averaged frequency, how many products the participants
will choose from your in the function determined potential assortment. 
Again, you have to define a <code>none</code> alternative, because <code>freqassort()</code> uses 
the <i>threshold</i> approach, meaning if the utility of one product is above 
the utility of <code>none</code>, it is marked as potential purchase option. 
While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, 
you specify the combination you are interested in <code>freqassort()</code>.</li>

<li><code>reach()</code>: Similar to <code>turf()</code>, <code>reach()</code> will
give you the averaged percentage of how many participants you can reach
(at least one of the products resemble a purchase option) with your in the function determined
potential assortment. <code>reach()</code> also uses the <i>threshold</i> approach (see above). While <code>turf()</code> calculates the reach and frequency for <b>all</b> combinations, you specify the combination you are interested in <code>reach()</code>.</li>

<li><code>marksim()</code>: runs market simulations (either share of preference or first choice rule), including the standard error, as well as the lower and upper confidence interval, which is
calculated according to the $mean +/- 1.96 x \frac{sd}{\sqrt(n)}$ (Orme, 2020, p. 94).</li>

@@

> <b>Important</b>: For both <code>reach()</code> and <code>freqassort()</code>, <code>noen</code> does not necessarily have to be the no-buy alternative but can be another alternative that should be exceeded.

@@

<li><code>ACBC</code>: Example data set with raw utilities of an ACBC
study conducted in Sawtooth. Price was linear-coded while the other
attributes were coded as part-worths.</li>

<li><code>ACBC_interpolate</code>: Example data set with raw utilities
of an ACBC study conducted in Sawtooth. Price was piecewise-coded,
another attribute was linear-coded while the other attributes were coded
as part-worths.</li>

<li><code>CBC</code>: Example data set with raw utilities of a CBC
study conducted in Sawtooth. All attributes were coded as
part-worth.</li>

<li><code>CBC_lin</code>: Example data set with raw utilities of a CBC
study conducted in Sawtooth. One attribute was linear coded while the
other attributes are part-worth coded.</li>

<li><code>MaxDiff</code>: Example data set with raw utilities of a
MaxDiff study conducted in Sawtooth.</li>
